---
title: "Regression Modeling" 
author: "Jonathan Salas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: kable
    fig_height: 6
    keep_md: true
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(ggplot2)
library(emmeans)
library(medrc)
library(aomisc)
library(sfsmisc)
knitr::opts_chunk$set(echo = F)
knitr::opts_knit$set(root.dir = "~/R_Projects/Dose_Response")
```

# Start with a clean slate

```{r echo = F}
rm(list = ls(all.names = TRUE))
```

# Import the cleaned data - Point to the correct raw data directory

```{r echo = F}
working_dat_dir <-"data/processed/working_dr.RData"
```

# Aesthetics

```{r echo = F}
blank.plot <- theme_bw() +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), #this theme section generates a blank canvas
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.title = element_blank(),
        legend.justification="top")
```

## Import Subject Data
```{r echo = F}
load(working_dat_dir)
```

# Regression Fitting

## Make Testing Data

We take the original data and label it "og", then we take the depth data from "og", subtract 4 from depth and label it's group "og_minus4). 

```{r}
test_dat_1 <- working_dat |> filter(voltage == 15, pulse_seq == "20x5", waveform == "unipolar") |>
  mutate(group = "og")
test_dat_2 <- working_dat |> filter(voltage == 15, pulse_seq == "20x5", waveform == "unipolar") |> 
  mutate(group = "og_minus4",
         depth = depth - 4)
```

```{r}
test_dat <- test_dat_1 |> full_join(test_dat_2)
```


## 15 kV Unipolar 20x5

### 2-Parameter Nonlinear Asymptotic Regression

#### Depth

```{r}
drm_depth_asymp_grouped_4 <- drm(
  depth ~ application_num,
  curveid = group,
  data = test_dat,
  fct = AR.2(names = c("Upper Limit", "Steepness"))
)
```

```{r}
summary(drm_depth_asymp_grouped_4)
```

```{r}
test_dat |>
  ggplot(data = _, aes(x = application_num, y = depth, group = group, color = group)) +
  geom_smooth(method = drm,
              method.args = list(fct = AR.2()),
              se = F) +
  geom_jitter(width = 0.2, size = 4) + 
  scale_x_continuous(
    labels = unique(working_dat$application_num),
    breaks = unique(working_dat$application_num)
  ) +
  ggtitle("15kV 20x5 Unipolar") +
  xlab("Applications") +
  ylab("Depth (mm)") +
  labs(caption = "Caption") + 
  coord_cartesian(ylim=c(5,20))+
  blank.plot 
#  theme(axis.text=element_text(size=40, face = "bold"),
#        axis.title=element_text(size=24,face="bold")) 

#ggsave("15kv20x5uni_depth.png",
#       path = "figures",
#       scale = 1,
#       width = 20,
#       height = 28,
#       units = "cm",
#       dpi = "retina",
#       limitsize = F)
```

### Summary Plot

#### Depth

```{r}
working_dat |>
  ggplot(data = _, aes(x = application_num, y = depth)) +
  geom_smooth(method = drm,
              method.args = list(fct = AR.2()),
              se = F) +
  geom_point(size = 4, aes(color = interaction(voltage,waveform,pulse_seq))) +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  coord_cartesian(ylim=c(0,25)) +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Depth (mm)") +
  labs(caption = "Caption") +
  blank.plot +
  theme(axis.text=element_text(size=30, face = "bold"),
        axis.title=element_text(size=24,face="bold")) 

ggsave("nls_applications_vs_depth.png",
       path = "figures",
       scale = 1,
       width = 50,
       height = 25,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# When were these files last rewritten?

```{r}
date()
```