---
title: "PULSE & VCAS Hemolysis Regressions"
author: "Jonathan Salas"
date: "Last Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: kable
    fig_height: 6
    keep_md: true
---

# Start with a clean slate

## Remove all objects

```{r echo = F, include=FALSE}
rm(list = ls(all.names = TRUE)) # Remove all starting code
```

## Detach Packages

```{r include=FALSE}
try(invisible(lapply(paste0('package:', names(sessionInfo()$otherPkgs)), detach, character.only=TRUE, unload=TRUE)), silent = T) # Detach Packages
```

# Load Libraries

```{r setup, include=FALSE}
library(MASS)
library(sfsmisc)
library(emmeans)
library(ggplot2)
library(cowplot)
library(dplyr)
knitr::opts_chunk$set(echo = F)
knitr::opts_knit$set(root.dir = "~/R_Projects/Dose_Response")
```

# Import the raw data - Point to the correct raw data directory

```{r}
raw_data_dir <- "data/processed/combined_hemolysis_dat.RData"
```

```{r}
load(raw_data_dir)
```

# Regression

## Set seed for reproducibility

We found that asymptotic confidence intervals changed with each computation, unless we set a seed within each emmeans code chunk. We also tested setting a global seed 

```{r}
seed <- 42494
```


## Make Regression Data

```{r}
reg_dat_15kV <- combined_hemolysis_perc_change |> 
  filter(data_event == "V 1 P R E D",
         waveform == "Uni 20x5 15kV" | waveform == "Uni 3x12x3 15kV" | waveform == "15kV 3x12 Uni")

reg_dat <- combined_hemolysis_perc_change |> 
  filter(data_event == "V 1 P R E D")
```


## Number of Applications vs. Lab Values - Percent Change from V0 -> V1

### Haptoglobin 

#### Robust Linear Regression

```{r}
rlm_haptoglobin <-
  rlm(
    serumhaptoglobin_serumhaptoglobin_bloodvalue_perc_change ~ sum_applications,
    data = reg_dat
  )
```

##### Post-Hoc

```{r}
summary(rlm_haptoglobin)
```

```{r}
plot(rlm_haptoglobin)
```

```{r}
set.seed(.GlobalEnv$seed)
emm_rlm_haptoglobin <-
  as.data.frame(emmeans::emmeans(rlm_haptoglobin,
                   ~ sum_applications,
                   at = list(sum_applications = c(25, 50, 75, 100, 125, 150)),
                   adjust = "mvt"))

emm_rlm_haptoglobin
```


##### Plot Results

```{r}
reg_dat |>
ggplot(
  aes(y = serumhaptoglobin_serumhaptoglobin_bloodvalue_perc_change, x = sum_applications)
) +
  geom_smooth(method = "rlm", se = F) +
  geom_point(aes(color = study, 
                 shape = waveform
                 ), size = 3) +
#  geom_errorbar(
#    data = emm_rlm_haptoglobin,
#    aes(
#      x = applications,
#      y = emmean,
#      ymin = asymp.LCL,
#      ymax = asymp.UCL
#    ),
#    width = .3
#  )  +
  labs(x = "Applications", y = "% of Baseline", title = "Serum Haptoglobin", caption = "Robust Linear Regression") +
  theme_cowplot(12)
```

### Bilirubin 

#### Robust Linear Regression



```{r}
rlm_bilirubin <-
  rlm(
    bilirubin_bilirubin_bloodvalue_perc_change ~ sum_applications,
    data = reg_dat
  )
```

##### Post-Hoc

```{r}
summary(rlm_bilirubin)
```

```{r}
plot(rlm_bilirubin)
```

```{r}
f.robftest(rlm_bilirubin, "sum_applications")
```

```{r}
set.seed(.GlobalEnv$seed)
emm_rlm_bilirubin <-
  as.data.frame(emmeans::emmeans(rlm_bilirubin,
                   ~ sum_applications,
                   at = list(sum_applications = c(25, 50, 75, 100, 125, 150)),
                   adjust = "mvt"))

emm_rlm_bilirubin
```

##### Plot Results

```{r}
ggplot(
  data = reg_dat,
  aes(y = bilirubin_bilirubin_bloodvalue_perc_change, x = sum_applications)
) +
  geom_smooth(method = "rlm", se = F) +
  geom_point(aes(color = subjectId, shape = waveform), size = 3) +
#  geom_errorbar(
#    data = emm_rlm_bilirubin,
#    aes(
#      x = applications,
#      y = emmean,
#      ymin = asymp.LCL,
#      ymax = asymp.UCL
#    ),
#    width = .3
#  )  +
    labs(x = "Applications", y = "% of Baseline", title = "Bilirubin", caption = "Robust Linear Regression") +
  theme_cowplot(12)
```

### Lactate Dehydrogenase 

#### Robust Linear Regression

```{r}
rlm_ldh <-
  rlm(
    ldh_ldh_bloodvalue_perc_change ~ sum_applications,
    data = reg_dat
  )
```

##### Post-Hoc

```{r}
summary(rlm_ldh)
```

```{r}
plot(rlm_ldh)
```

```{r}
f.robftest(rlm_ldh, "sum_applications")
```

```{r}
set.seed(.GlobalEnv$seed)
emm_rlm_ldh <-
  as.data.frame(emmeans::emmeans(rlm_ldh,
                   ~ sum_applications,
                   at = list(sum_applications = c(25, 50, 75, 100, 125, 150)),
                   adjust = "mvt"))

emm_rlm_ldh
```


##### Plot Results

```{r}
ggplot(
  data = reg_dat,
  aes(y = ldh_ldh_bloodvalue_perc_change, x = sum_applications)
) +
  geom_smooth(method = "rlm", se = F) +
  geom_point(aes(color = subjectId, shape = waveform), size = 3) +
#  geom_errorbar(
#    data = emm_rlm_haptoglobin,
#    aes(
#      x = applications,
#      y = emmean,
#      ymin = asymp.LCL,
#      ymax = asymp.UCL
#    ),
#    width = .3
#  )  +
    labs(x = "Applications", y = "% of Baseline", title = "Lactate Dehydrogenase", caption = "Robust Linear Regression") +
  theme_cowplot(12)
```

### Potassium

#### Robust Linear Regression

```{r}
rlm_K <-
  rlm(
    potassium_potassium_bloodvalue_perc_change ~ sum_applications,
    data = reg_dat
  )
```

##### Post-Hoc

```{r}
summary(rlm_K)
```

```{r}
plot(rlm_K)
```

```{r}
f.robftest(rlm_K, "sum_applications")
```

```{r}
set.seed(.GlobalEnv$seed)
emm_rlm_K <-
  as.data.frame(emmeans::emmeans(rlm_K,
                   ~ sum_applications,
                   at = list(sum_applications = c(25, 50, 75, 100, 125, 150)),
                   adjust = "mvt"))

emm_rlm_K
```

##### Plot Results

```{r}
ggplot(
  data = reg_dat,
  aes(y = potassium_potassium_bloodvalue_perc_change, x = sum_applications)
) +
  geom_smooth(method = "rlm", se = F) +
  geom_point(aes(color = subjectId, shape = waveform), size = 3) +
#  geom_errorbar(
#    data = emm_rlm_haptoglobin,
#    aes(
#      x = applications,
#      y = emmean,
#      ymin = asymp.LCL,
#      ymax = asymp.UCL
#    ),
#    width = .3
#  )  +
    labs(x = "Applications", y = "% of Baseline", title = "Potassium", caption = "Robust Linear Regression") +
  theme_cowplot(12)
```



# 15kV ONLY

### Haptoglobin 

#### Robust Linear Regression

```{r}
rlm_haptoglobin_15kV <-
  rlm(
    serumhaptoglobin_serumhaptoglobin_bloodvalue_perc_change ~ sum_applications,
    data = reg_dat_15kV
  )
```

##### Post-Hoc

```{r}
summary(rlm_haptoglobin_15kV)
```

```{r}
plot(rlm_haptoglobin_15kV)
```

```{r}
set.seed(.GlobalEnv$seed)
emm_rlm_haptoglobin_15kV <-
  as.data.frame(emmeans::emmeans(rlm_haptoglobin_15kV,
                   ~ sum_applications,
                   at = list(sum_applications = c(25, 50, 75, 100, 125, 150)),
                   adjust = "mvt"))

emm_rlm_haptoglobin_15kV
```


##### Plot Results

```{r}
reg_dat_15kV |>
ggplot(
  aes(y = serumhaptoglobin_serumhaptoglobin_bloodvalue_perc_change, x = sum_applications)
) +
  geom_smooth(method = "rlm", se = F) +
  geom_point(aes(color = study, 
                 shape = waveform
                 ), size = 3) +
#  geom_errorbar(
#    data = emm_rlm_haptoglobin,
#    aes(
#      x = applications,
#      y = emmean,
#      ymin = asymp.LCL,
#      ymax = asymp.UCL
#    ),
#    width = .3
#  )  +
  labs(x = "Applications", y = "% of Baseline", title = "Serum Haptoglobin - 15kV", caption = "Robust Linear Regression") +
  theme_cowplot(12)
```

### Bilirubin 

#### Robust Linear Regression

```{r}
rlm_bilirubin_15kV <-
  rlm(
    bilirubin_bilirubin_bloodvalue_perc_change ~ sum_applications,
    data = reg_dat_15kV
  )
```

##### Post-Hoc

```{r}
summary(rlm_bilirubin_15kV)
```

```{r}
plot(rlm_bilirubin_15kV)
```

```{r}
set.seed(.GlobalEnv$seed)
emm_rlm_bilirubin_15kV <-
  as.data.frame(emmeans::emmeans(rlm_bilirubin_15kV,
                   ~ sum_applications,
                   at = list(sum_applications = c(25, 50, 75, 100, 125, 150)),
                   adjust = "mvt"))

emm_rlm_bilirubin_15kV
```


##### Plot Results

```{r}
reg_dat_15kV |>
ggplot(
  aes(y = bilirubin_bilirubin_bloodvalue_perc_change, x = sum_applications)
) +
  geom_smooth(method = "rlm", se = F) +
  geom_point(aes(color = study, 
                 shape = waveform
                 ), size = 3) +
#  geom_errorbar(
#    data = emm_rlm_haptoglobin,
#    aes(
#      x = applications,
#      y = emmean,
#      ymin = asymp.LCL,
#      ymax = asymp.UCL
#    ),
#    width = .3
#  )  +
  labs(x = "Applications", y = "% of Baseline", title = "Bilirubin - 15kV", caption = "Robust Linear Regression") +
  theme_cowplot(12)
```

# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# Detach Packages before moving on

```{r}
invisible(lapply(paste0('package:', names(sessionInfo()$otherPkgs)), detach, character.only=TRUE, unload=TRUE)) # Detach Packages
```

# When were these files last rewritten?

```{r}
date()
```