---
title: "Dose-Response Descriptive Statistics" 
author: "Jonathan Salas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: kable
    fig_height: 6
    keep_md: true
---

```{r setup, include=FALSE}
library(knitr)
library(janitor)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
knitr::opts_chunk$set(echo = F)
knitr::opts_knit$set(root.dir = "~/R_Projects/Dose_Response")
```

# Start with a clean slate

```{r echo = F}
rm(list = ls(all.names = TRUE))
```

# Import the cleaned data - Point to the correct raw data directory

```{r echo = F}
working_dat_dir <-"data/processed/working_dr.RData"
```

# Aesthetics

```{r echo = F}
blank.plot <- theme_bw() +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), #this theme section generates a blank canvas
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.title = element_blank(),
        legend.justification="top")
```

## Import Subject Data
```{r echo = F}
load(working_dat_dir)
```

# Descriptive Statistics

## Summary Table of Subjects 
```{r How many subjects got which waveform, pulse sequence, and input voltage, echo = F}
working_dat |>
  count(waveform, voltage, pulse_seq) |> left_join(
    # Add in basic stats for depth/diameter
    working_dat |> group_by(waveform, voltage, pulse_seq) |>
      summarise(
        median_depth = median(depth, na.rm = T),
        IQR_depth = IQR(depth, na.rm = T),
        median_diameter = median(diameter, na.rm = T),
        IQR_diameter = IQR(diameter, na.rm = T),
        median_depth_per_width = median(depth_per_width, na.rm = T),
        IQR_depth_per_width = IQR(depth_per_width, na.rm = T)
      )
  )
```

# Plots

## Depth

### Depth Dose-Response - Line Plots

```{r echo = F}
working_dat |>
  ggplot(data = _, aes(
    x = application_num,
    y = depth,
    group = id,
    color = id
  )) +
  geom_point(size = 3) +
  geom_line() +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Depth (mm)") +
  labs(caption = "Caption") +
  blank.plot +
  theme(axis.text=element_text(size=30, face = "bold"),
        axis.title=element_text(size=24,face="bold")) 

ggsave("raw_applications_vs_depth.png",
       path = "figures",
       scale = 1,
       width = 50,
       height = 25,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

### Depth Dose-Response - Smoothed Line Plots

```{r echo = F}
working_dat |>
  ggplot(data = _, aes(x = application_num, y = depth)) +
  geom_smooth(span = 10) +
  geom_point(aes(color=id), size = 3) +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Depth (mm)") +
  labs(caption = "Caption") +
  blank.plot
```

## Diameter Dose-Response

### Diameter line plots 

```{r}
working_dat |>
  ggplot(data = _, aes(
    x = application_num,
    y = diameter,
    group = id,
    color = id
  )) +
  geom_point(size = 4) +
  geom_line() +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Diameter (mm)") +
  labs(caption = "Caption") +
  blank.plot +
  theme(axis.text=element_text(size=30, face = "bold"),
        axis.title=element_text(size=24,face="bold")) 

ggsave("raw_applications_vs_diameter.png",
       path = "figures",
       scale = 1,
       width = 50,
       height = 25,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

### Diameter Dose-Response - Smoothed Line Plots

```{r}
working_dat |>
  ggplot(data = _, aes(x = application_num, y = diameter)) +
  geom_smooth(span = 10) +
  geom_point(aes(color=id), size = 3) +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Diameter (mm)") +
  labs(caption = "Caption") +
  blank.plot
```

## Depth/Diameter Ratio

### Depth/Diameter Ratio line plots 

```{r}
working_dat |>
  ggplot(data = _, aes(
    x = application_num,
    y = depth_per_width,
    group = id,
    color = id
  )) +
  geom_point(size = 4) +
  geom_line() +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Depth/Diameter Ratio") +
  labs(caption = "Caption") +
  blank.plot +
  theme(axis.text=element_text(size=30, face = "bold"),
        axis.title=element_text(size=24,face="bold")) 

ggsave("raw_depth_diameter_ratio.png",
       path = "figures",
       scale = 1,
       width = 50,
       height = 25,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```


### Depth/Diameter Ratio LOESS line plots 

```{r}
working_dat |>
  ggplot(data = _, aes(
    x = application_num,
    y = depth_per_width
  )) +
  geom_point(aes(color = id), size = 4) +
  geom_smooth(span = 10) +
  facet_wrap( ~ voltage + waveform + pulse_seq, nrow = 1) +
  scale_x_continuous(labels = working_dat$application_num,
                     breaks = working_dat$application_num) +
  scale_color_discrete(guide = "none") +
  ggtitle("Title") +
  xlab("Applications") +
  ylab("Depth/Diameter Ratio") +
  labs(caption = "Caption") +
  blank.plot
```


# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# When were these files last rewritten?

```{r}
date()
```