---
title: "Regression Modeling" 
author: "Jonathan Salas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: kable
    fig_height: 6
    keep_md: true
---

```{r setup, include=FALSE}
library(knitr)
library(sfsmisc)
library(emmeans)
library(sandwich)
library(aomisc)
library(ggplot2)
library(dplyr)
knitr::opts_chunk$set(echo = F)
knitr::opts_knit$set(root.dir = "~/R_Projects/Dose_Response")
```

# Start with a clean slate

```{r echo = F}
rm(list = ls(all.names = TRUE))
```

# Import the cleaned data - Point to the correct raw data directory

```{r echo = F}
working_dat_dir <-"data/processed/working_dr.RData"
```

# Aesthetics

```{r echo = F}
blank.plot <- theme_bw() +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), #this theme section generates a blank canvas
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.title = element_blank(),
        legend.justification="top")
```

## Import Subject Data
```{r echo = F}
load(working_dat_dir)
```

# Regression Fitting

## 15 kV Unipolar 3x12x3

### Depth

#### Model Selection

```{r}
drm_depth_asymp_5 <- drm(
  depth ~ application_num,
  data = working_dat,
  subset = (voltage == 15 &
              pulse_seq == "3x12x3" & 
              waveform == "unipolar"),
  fct = AR.2(names = c("Upper Limit", "Steepness"))
)
```

```{r}
mselect(
  drm_depth_asymp_5,
  list(
    L.3(), #L.3 lower limit at dose 0 is fixed at 0
    LL.3(), #LL.3 lower limit at dose 0 is fixed at 0
    LL2.3(), #LL2.3 lower limit at dose 0 is fixed at 0
    AR.2(), #AR.2 lower limit at dose 0 is fixed at 0
    MM.2() #MM.2 lower limit at dose = 0 is fixed at 0
  ),
  linreg = TRUE
)
```

#### 3-Parameter Log-Logistic Regression

```{r}
drm_depth_5 <- drm(
  depth ~ application_num,
  data = working_dat,
  subset = (voltage == 15 &
              pulse_seq == "3x12x3" & 
              waveform == "unipolar"),
  fct = LL.3(names = c("b", "Upper Limit", "Inflection"))
)
```

##### Post-Hoc

```{r}
summary(drm_depth_5)
```

```{r}
PR(drm_depth_5, c(seq_along(1:10)))
```

#### Plotting

```{r}
working_dat |>
  filter(voltage == 15, pulse_seq == "3x12x3", waveform == "unipolar") |>
  ggplot(data = _, aes(x = application_num, y = depth)) +
  geom_smooth(method = drm,
              method.args = list(fct = LL.3()),
              se = F) +
  geom_jitter(width = 0.2, size = 4, na.rm = T) + 
  scale_x_continuous(
    labels = unique(working_dat$application_num),
    breaks = unique(working_dat$application_num)
  ) +
  ggtitle("15kV 3x12x3 Unipolar") +
  xlab("Applications") +
  ylab("Depth (mm)") +
#  # labs(caption = "Caption") + 
  coord_cartesian(ylim=c(3, 18))+
  blank.plot 
#  theme(axis.text=element_text(size=40, face = "bold"),
#        axis.title=element_text(size=24,face="bold")) 

#ggsave("15kv3x12x3uni_depth.png",
#       path = "figures",
#       scale = 1,
#       width = 20,
#       height = 28,
#       units = "cm",
#       dpi = "retina",
#       limitsize = F)
```

### Full Depth Curve

#### Model Selection 

```{r}
drm_full_depth_ll_5 <- drm(
  depth ~ pulses,
  data = full_curve_3x12x3,
  fct = LL2.4()
)
```

```{r}
mselect(
  drm_full_depth_ll_5,
  list(
    L.3(),
    L.4(),
    L.5(),
    LL.3(),
    LL2.3(),
    LL.4(),
    LL2.4(),
    LL.5(),
    LL2.5(),
    W1.4(),
    W2.4()
  ),
  linreg = T,
  icfct = BIC
)
```

#### Four-Parameter Weibull Type 1 

https://setac.onlinelibrary.wiley.com/doi/10.1002/etc.7

The present study considers four different classes of sigmoidal dose–response models with horizontal asymptotes or limits at the extremes of the dose range. It will be shown below that these four classes encompass many of the dose–response models that are useful to ecotoxicologists. The classes are called log-logistic models, log-normal models, Weibull-1 models, and Weibull-2 models

https://www.r-bloggers.com/2019/11/five-parameters-logistic-regression/

```{r}
drm_full_depth_5 <- drm(
  depth ~ pulses,
  data = full_curve_3x12x3,
#  fct = LL2.5(names = c("Slope", "Lower Limit", "Upper Limit", "C","Asymmetry"),
#              fixed = c(NA,NA,NA,NA,NA))
  fct = W1.4(names = c("b", "Lower Limit", "Upper Limit", "e")) 
)
```

##### Post-Hoc

```{r}
summary(drm_full_depth_5)
```

```{r}
depth_fitted <- as.data.frame(cbind(
  pulses = full_curve_3x12x3$pulses,
  predict(
    drm_full_depth_5,
    interval = "confidence",
    level = 0.95,
    vcov = sandwich
  )
)) |> unique()

EC50_pulses_pred <- as.data.frame(ED(drm_full_depth_5, 50, interval = "delta", vcov = sandwich))

EC50_depth_pred <- as.data.frame(cbind("EC50_pulses" = EC50_pulses_pred$Estimate, (t(
  predict(
    #Predict depth as EC50 and return robust confidence intervals
    drm_full_depth_5,
    newdata = data.frame(pulses = EC50_pulses_pred$Estimate),
    interval = "confidence",
    vcov = sandwich
  )
)))) |> rename("EC50_depth" = Prediction)
```

#### Plotting 

```{r}
ggplot(data = NULL) +
  geom_smooth(
    data = full_curve_3x12x3,
    aes(x = pulses, y = depth),
    method = drm,
    method.args = list(fct = W1.4()),
    se = F,
    linetype = "dashed",
    color = "black"
  ) +
  geom_jitter(data = full_curve_3x12x3,
              aes(x = pulses, y = depth, color = pulses),
              size = 4) +
  scale_colour_distiller(palette = "Spectral", direction = 1) +
  geom_errorbar(
    data = depth_fitted,
    aes(
      x = pulses,
      y = Prediction,
      ymin = Lower,
      ymax = Upper
    ),
    width = .3
  ) +
  geom_point(
    data = EC50_depth_pred,
    aes(x = EC50_pulses, y = EC50_depth),
    size = 14,
    shape = 6,
    fill = "white",
    color = "black"
  ) +
  geom_point(data = EC50_depth_pred,
             aes(x = EC50_pulses, y = EC50_depth),
             size = 2) +
  geom_segment(data = EC50_pulses_pred,
               aes(
                 x = Lower,
                 y = 1,
                 xend = Upper,
                 yend = 1
               ),
               color = "blue") +
  scale_x_continuous(
    labels = c(
      unique(full_curve_3x12x3$pulse_seq),
      unique(full_curve_3x12x3$pulses[full_curve_3x12x3$pulses > 108])
    ),
    breaks = unique(full_curve_3x12x3$pulses),
    transform = "log",
    guide = guide_axis(angle = -45)
  ) +
  labs(
    x = "Log(Pulses)",
    y = "Depth (mm)",
    title = "4-Parameter Weibull Type 1 - 3x12x3",
    caption = "Regression line with Robust 95% confidence Intervals and Observed Values"
  ) +
  blank.plot +
  theme(
    axis.text = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 24, face = "bold")
  ) 

ggsave("15kv3x12x3uni_full_depth.png",
       path = "figures",
       scale = 1,
       width = 42,
       height = 20,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

### Diameter

#### Model Selection

```{r}
drm_diameter_l4_5 <- drm(
  diameter ~ application_num,
  data = full_curve_3x12x3,
  fct = L.3()
)
```

```{r}
mselect(
  drm_diameter_l4_5,
  list(
    L.3(),
    L.4(),
    LL.3(),
    LL2.3(),
    LL.4(),
    LL2.4(),
    W1.4(),
    W2.4()
  ),
  linreg = T,
  icfct = BIC
)
```

#### Robust Log-Linear Regression 

```{r}
rlm_diameter_5 <- rlm(
  diameter ~ log(pulses),
  data = full_curve_3x12x3
)
```

```{r}
BIC(drm_diameter_l4_5)
BIC(rlm_diameter_5)
```

##### Post-Hoc 

```{r}
summary(rlm_diameter_5)
```

```{r}
confint.default(object = rlm_diameter_5, parm = "log(pulses)", level = 0.95)
```

I need the median of the fitted function not the quantiles of the observed data

```{r}
#diameter = m*log(pulse) + intercept, so exp((diameter - intercept)/m) = pulse
intercept <- coef(rlm_diameter_5)[["(Intercept)"]]
m <- coef(rlm_diameter_5)[["log(pulses)"]]

EC50_diameter <- quantile(full_curve_3x12x3$diameter, 0.5)
EC50_pulse <- exp((EC50_diameter-intercept)/m)
```

#### Plotting

```{r}
diameter_fitted <- as.data.frame(cbind(
  pulses = full_curve_3x12x3$pulses,
  predict(
    rlm_diameter_5,
    interval = "confidence",
    level = 0.95,
    vcov = sandwich
  )
)) |> unique()
```

```{r}
ggplot(data = NULL) +
  geom_smooth(
    data = full_curve_3x12x3,
    aes(x = pulses, y = diameter),
    method = rlm,
    formula = y ~ x,
    se = F,
    linetype = "dashed",
    color = "black"
  ) +
  geom_jitter(data = full_curve_3x12x3,
              aes(x = pulses, y = diameter, color = pulses),
              size = 4) +
  scale_colour_distiller(palette = "Spectral", direction = 1) +
    geom_errorbar(
    data = diameter_fitted,
    aes(
      x = pulses,
      y = fit,
      ymin = lwr,
      ymax = upr
    ),
    width = .3
  ) +
  geom_point(
    data = NULL,
    aes(x = EC50_pulse, y = EC50_diameter),
    size = 14,
    shape = 6,
    fill = "white",
    color = "black"
  ) +
  geom_point(data = NULL,
             aes(x = EC50_pulse, y = EC50_diameter),
             size = 2) +
#  geom_segment(data = EC50_pulses_pred,
#               aes(
#                 x = lwr,
#                 y = 1,
#                 xend = upr,
#                 yend = 1
#               ),
#               color = "blue") +
  scale_x_continuous(
    labels = c(
      unique(full_curve_3x12x3$pulse_seq),
      unique(full_curve_3x12x3$pulses[full_curve_3x12x3$pulses > 108])
    ),
    breaks = unique(full_curve_3x12x3$pulses),
    transform = "log",
    guide = guide_axis(angle = -45)
  ) +
  labs(
    x = "Log(Pulses)",
    y = "Diameter (mm)",
    title = "Robust Linear Regression - 3x12x3",
    caption = "Regression line with Robust 95% confidence Intervals and Observed Values"
  ) +
  blank.plot +
  theme(
    axis.text = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 24, face = "bold")
  ) 

ggsave("15kv3x12x3uni_full_diameter.png",
       path = "figures",
       scale = 1,
       width = 42,
       height = 20,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

### Depth/Diameter Ratio

```{r}
drm_depth_ratio_5 <- drm(
  diameter ~ pulses,
  data = full_curve_3x12x3,
  fct = AR.2(names = c("Upper Limit", "Steepness"))
)
```

#### Model Selection

```{r}
mselect(
  drm_depth_ratio_5,
  list(
    L.3(), #L.3 lower limit at dose 0 is fixed at 0
    LL.3(), #LL.3 lower limit at dose 0 is fixed at 0
    LL2.3(), #LL2.3 lower limit at dose 0 is fixed at 0
    AR.2(), #AR.2 lower limit at dose 0 is fixed at 0
    MM.2() #MM.2 lower limit at dose = 0 is fixed at 0
  ),
  linreg = TRUE
)
```

#### 3-Parameter Log-Logistic Regression

```{r}
drm_depth_ratio_5 <- drm(
  depth_per_width ~ pulses,
  data = full_curve_3x12x3,
  fct = LL2.3())
```

```{r}
summary(drm_depth_ratio_5)
```

#### Plotting 

```{r}
full_curve_3x12x3 |>
  ggplot(data = _, aes(x = pulses, y = depth_per_width)) +
  geom_jitter(width = 0.2,
              size = 4,
              na.rm = T) +
  geom_smooth(method = "drm",
              method.args = list(fct = LL2.3()),
              se = F,
  ) +
  #  geom_smooth(method = drm,
  #              method.args = list(fct = AR.2()),
  #              se = F) +
  scale_x_continuous(
    labels = c(
      unique(full_curve_3x12x3$pulse_seq),
      unique(full_curve_3x12x3$pulses[full_curve_3x12x3$pulses > 108])
    ),
    breaks = unique(full_curve_3x12x3$pulses),
#    transform = "log",
    guide = guide_axis(angle = -45)
  ) +
  ggtitle("15kV 3x12x3") +
  xlab("Pulses") +
  ylab("Depth per Diameter") +
  #  # labs(caption = "Caption") +
  #  coord_cartesian(ylim=c(10,20)) +
  blank.plot 
```

# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# When were these files last rewritten?

```{r}
date()
```